Deeply Virtual Compton Scattering measurement off bound protons

### 2018-12-21 eg6-letters/incoherent/publication_version/incoherent_prl.tex
update the paper after editing the figures

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
\begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts
are slightly wider than those previously used for free proton experiments~%
\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
appear to be stable as a function of cut width and we saw no sizable effect 
that could be related to the initial momentum of the nucleons. We also rejected 
events where a $\pi^0$ was identified by the invariant mass of two photons. At 
the end of this selection process, about 30k events passed all the 
requirements.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{incoh_exc_cuts_final.pdf}
\caption{The distributions from left to right and from top to bottom are: 
   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
   final-state system. The incoherent DVCS exclusivity cuts are represented by 
   the vertical red-dashed lines. The black distributions represent the 
   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
   distributions represent the incoherent DVCS events that passed all of these 
   cuts except the quantity plotted.}
\label{fig:kin-cuts}
\end{figure}

%background
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
   bins (bottom row). The error bars represent the statistical uncertainties.  
   The gray bands represent the systematic uncertainties, including the 
   normalization uncertainties. The black curves are the results of our fits 
   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
contributions to systematic uncertainties on these fits are from the choice of 
the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
uncertainties sum up to less than 10\% for all data points and thus always 
remain significantly smaller than the statistical uncertainities.

>>>>

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. First, 
events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
than 2 GeV to avoid the nucleon resonance region. The squared transferred 
momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
the incoming and outgoing photons, was required to be greater than a minimum 
kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
\begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass). We specifically used the kinematics of the photons to determine 
$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
ensured the exclusivity of the incoherent DVCS events by imposing a series of 
constraints based on the four-momentum conservation in the reaction 
$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
angle $\theta$ between the measured photon and the missing momentum of the 
$e'p'$ system. The experimental data for the most relevant exclusivity 
variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
the nucleons in the helium nucleus, these cuts are slightly wider than those 
previously used for free proton experiments~\cite{Girod:2007aa}. After the 
corrections discussed below, the asymmetries appear to be stable as a function 
of cut width and we saw no sizable effect that could be related to the initial 
momentum of the nucleons. We also rejected events where a $\pi^0$ was 
identified by the invariant mass of two photons. At the end of this selection 
process, about 30k events passed all the requirements.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{incoh_exc_cuts_final.pdf}
\caption{The distributions from left to right and from top to bottom are: 
   $\Delta \phi$, missing energy, missing mass squared and the cone angle 
   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
   final-state system. The incoherent DVCS exclusivity cuts are represented by 
   the vertical red-dashed lines. The black distributions represent the 
   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
   distributions represent the incoherent DVCS events that passed all of these 
   cuts except the quantity plotted.}
\label{fig:kin-cuts}
\end{figure}

%background
\begin{figure*}[t!]
\includegraphics[width=13.9cm]{incoherent_ALU_phi_t.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$ for different $t$ 
   bins.  The error bars represent the statistical uncertainties. The gray 
   bands represent the systematic uncertainties, including the normalization 
   uncertainties. The black curves are the results of our fits with the form 
   $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
\label{fig:alu}
\end{figure*}

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $t$ (integrated over the full $Q^{2}$ and $x_{B}$ ranges).  
The curves on the plots are fits of the form $\frac{a_{0}~\sin(\phi)}{1+ 
a_{1}~\cos(\phi)}$.  The main contributions to systematic uncertainties on 
these fits are from the choice of the DVCS exclusivity cuts (6\%) and the large 
bin size (7\%). The systematic uncertainties sum up to less than 10\% for all 
data points and thus always remain significantly smaller than the statistical 
uncertainities.
